Adversarial Variational Optimization\\ of Non-Differentiable Simulators

### 2018-02-11 colt/avo.tex
save

The top left plot in Figure~\ref{fig:weinberg} illustrates the resulting
proposal distributions $q(\bftheta|\bfpsi)$ after
AVO. We see that the proposal distribution concentrates
in the neighborhood of $\bftheta^*$.
Despite the width of the resulting proposal distribution with respect to $\bftheta^*$,
the synthetic data closely match with the observed data, as shown
in the top right plot of  Figure~\ref{fig:weinberg}. This suggests either a relatively flat
landscape around $\bftheta^*$ or that the observed data can in this case also be
reproduced with the  predictive distribution $\qxpsi$.
Finally, the bottom plot of Figure~\ref{fig:weinberg} shows that for both
the variational upper bound $-U_d$ fall
towards $0$, which indicates  convergence towards a distribution that the critic
cannot distinguish from the true distribution.

>>>>

The top left plot in Figure~\ref{fig:weinberg} illustrates the resulting
proposal distributions $q(\bftheta|\bfpsi)$ after
AVO. We see that the proposal distribution concentrates
in the neighborhood of $\bftheta^*$.
Despite the width of the resulting proposal distribution with respect to $\bftheta^*$,
the synthetic data closely match with the observed data, as shown
in the top right plot of  Figure~\ref{fig:weinberg}. This suggests either a relatively flat
landscape around $\bftheta^*$ or that the observed data can in this case also be
reproduced through a different predictive distribution $\qxpsi$.
Finally, the bottom plot of Figure~\ref{fig:weinberg} shows that for both
the variational upper bound $-U_d$ fall
towards $0$, which indicates  convergence towards a distribution that the critic
cannot distinguish from the true distribution.
